Estimate RSV onset and peak timing

### 2023-01-10 RSV_timing_explain/RSV_timing_tutorial.Rmd
minor change

$$X_t=\mu+R\cos(ft+d)+e_t$$
Where 
\
$X_t$ is the time-series contains a periodic (cyclic) component.
\
$\mu$ is mean of the series.
\
$R$ is the amplitude of seasonality.
\
$f=\frac{1}{period}$ is the frequency of the periodic.
\
$d$ is the phase or horizontal offset.
\
$e_t$ is the random error (noise) of the series.
\
$t$ is the time step

@@

#other series shifted by 3 months
 xt2a=amp1*cos(2*3.14159*t*freq+1)

@@

```{r, echo=T}
 plot(t, xt1,type="l", lwd=3, xaxt="n",bty="l",
      ylab="Cases of RSV", xlab="Month(n)", 
      ylim=range(c(xt1,xt2)))
 lines(t,xt2,col="red")
```

>>>>

$$X_t=\mu+R\cos(2\pi ft+d)+e_t$$
Where 
\
$X_t$ is the time-series contains a periodic (cyclic) component.
\
$\mu$ is mean of the series.
\
$R$ is the amplitude of seasonality.
\
$f=\frac{1}{period}$ is the frequency of the periodic.
\
$d$ is the phase or horizontal offset.
\
$e_t$ is the random error (noise) of the series.
\
$t$ is the time step

@@

#other series shifted by 2 months
 xt2a=amp1*cos(2*3.14159*t*freq+1)

@@

```{r, echo=T}
 plot(t, xt1,type="l", lwd=3, xaxt="n",bty="l",
      ylab="Cases of RSV", xlab="Month(n)", 
      ylim=range(c(xt1,xt2)))
 lines(t,xt2,col="red")
```
## Investigate the epidemic characteristics of the pseudo-RSV time-serieses

This is based on the prior knowledge that RSV has an annual cycle in temperate regions. For other viruses or RSV circulation in other climate, you should consider using wavelet analysis to identify the periodicity first.

### Create the needed harmonic variables with 12 month periods
```{r harm1, echo=TRUE}
t<-1:120
#Create harmonic variables
sin12=sin(2*pi*t/12)
cos12=cos(2*pi*t/12)
```

### Fit a simple poisson regression with 12 month period
